Data_visualization

### 2018-09-03 Rmd/Data_visualization_no_internet.Rmd
changes

#There are 3 crosses were seeds were lost (2,7,9)
#load libraries
library(reshape2)
library(ggplot2)
library(dplyr)
library(gridExtra)
library(grid)
library(lattice)
#read data and cleaning
pein_seed_set_final <- read.csv("Data/pein_seed_set_final.csv")
pein_seed_set_final=pein_seed_set_final[,-1]
#load the palette for all the 4 plots
cbPalette <- c( "#56B4E9","#E69F00", "#999999", "#009E73")
#Colur per family

a <- ggplot(pein_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
  labs(title="Petunia integrifolia",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x =element_blank())+
  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")

@@

#Colur per family
#Different colour per family
b <- ggplot(caan_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
  labs(title="Capsicum annuum",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x =element_blank())+
  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")

@@

soly_seed_set_final <- read.csv("Data/soly_seed_set_final.csv")
soly_seed_set_final=soly_seed_set_final[,-1]

cbPalette <- c( "#56B4E9","#E69F00", "#999999", "#009E73")
#Different colour per family
c <- ggplot(soly_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
  labs(title="Solanum lycopersicum",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")

@@

some_seed_set_final <- read.csv("Data/some_seed_set_final.csv")
some_seed_set_final=some_seed_set_final[,-1]

#Different colour per family
d <- ggplot(some_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
  labs(title="Solanum melongena",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")

@@

brol_seed_set_final <- read.csv("Data/brol_seed_set_final.csv")
brol_seed_set_final=brol_seed_set_final[,-1]
#Different colour per family
a <- ggplot(brol_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
  labs(title="Brassica oleracea",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x =element_blank())+
  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")

@@

#Different colour per family
b <- ggplot(brra_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
  labs(title="Brassica rapa",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x =element_blank())+
  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")

@@

ersa_seed_set_final <- read.csv("Data/ersa_seed_set_final.csv")
ersa_seed_set_final=ersa_seed_set_final[,-1]

#Different colour per family
c <- ggplot(ersa_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
  labs(title="Eruca versicaria",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")

@@

sial_seed_set <- read.csv("Data/sial_seed_set.csv", sep=";")
sial_seed_set <- filter(sial_seed_set, Treatment!="RARA 100%" & Treatment!="RARA 50%"& Treatment!="COSA 50%"& Treatment!="COSA 100%" )

#adding the focal species, first 50%
Species <- rep("SIAL", 10)
Treatment <- rep("SIAL 50%", 10)
Treatment.number <- seq(1:10)
Seed.production <- rep(0, 10)
sial_50 <- data.frame(Species,Treatment, Treatment.number, Seed.production)
#adding the focal species, 100%
Species <- rep("SIAL", 10)
Treatment <- rep("SIAL 100%", 10)
Treatment.number <- seq(1:10)
Seed.production <- rep(0, 10)
sial_100<-  data.frame(Species,Treatment, Treatment.number, Seed.production)
#Order from lower to higher values the average, to plot it nicely
colnames(sial_seed_set)[1] <- "Species"
colnames(sial_seed_set)[2] <- "Treatment"
colnames(sial_seed_set)[3] <- "Treatment.number"
colnames(sial_seed_set)[4] <- "Seed.production"
sial_seed_set <- rbind(sial_seed_set, sial_50, sial_100)
sial_seed_set$Treatment<- as.character(sial_seed_set$Treatment)
sial_seed_set <- sial_seed_set[order(sial_seed_set$Treatment),]

#Organizing with just 50% and cross, self, flower control and control on a side

library(stringr)
sial_seed_set_div <- str_split_fixed(as.character(sial_seed_set$Treatment), " ", 2)
sial_seed_set_div <- data.frame(sial_seed_set_div, stringsAsFactors = F)
colnames(sial_seed_set_div)=c("non_focal","percentage")
sial_seed_set_bind <- cbind(sial_seed_set,sial_seed_set_div)
sial_seed_set_bind <- filter(sial_seed_set_bind, percentage!="100%")

#Because I want to give it specifically order I do it separately
#pein_seed_set_common <- filter(sial_seed_set_bind, non_focal %in% c("CROSS", "SELF","CONTROL","FLOWER"))

sial_seed_set_cross <- filter(sial_seed_set_bind, non_focal %in% c("Cross"))
sial_seed_set_self <- filter(sial_seed_set_bind, non_focal %in% c("Self"))
sial_seed_set_control <- filter(sial_seed_set_bind, non_focal %in% c("Control"))
sial_seed_set_flower <- filter(sial_seed_set_bind, non_focal %in% c("Flower"))

#Changing 0 for NA'S FOCAL species

# I HAVENT BEEN ABLE TO WORK OUT ALL AT THE SAME TIME SO i DO IOT SEPARATELY
sial_seed_set_bind=sial_seed_set_bind[sial_seed_set_bind$non_focal!=c("Cross"),]
sial_seed_set_bind=sial_seed_set_bind[sial_seed_set_bind$non_focal!=c("Self"),]
sial_seed_set_bind=sial_seed_set_bind[sial_seed_set_bind$non_focal!=c("Control"),]
sial_seed_set_bind=sial_seed_set_bind[sial_seed_set_bind$non_focal!=c("Flower"),]

sial_seed_set_final<-rbind(sial_seed_set_bind,sial_seed_set_cross, sial_seed_set_self, sial_seed_set_control,
                           sial_seed_set_flower)
#deleting extra columns used for data formating
sial_seed_set_final=sial_seed_set_final[,-c(5,6)]
#adding NA'S to the focal species
sial_seed_set_final[sial_seed_set_final$Treatment==c("SIAL 50%"),4] <- NA

#changing non_focal species name
sial_seed_set_final$Treatment=as.character(sial_seed_set_final$Treatment)
sial_seed_set_final$Family[sial_seed_set_final$Treatment=="BROL 50%"] <- "Brassicaceae"
sial_seed_set_final$Family[sial_seed_set_final$Treatment=="BRRA 50%"] <- "Brassicaceae"
sial_seed_set_final$Family[sial_seed_set_final$Treatment=="SIAL 50%"] <- "Brassicaceae"
sial_seed_set_final$Family[sial_seed_set_final$Treatment=="ERSA 50%"] <- "Brassicaceae"
sial_seed_set_final$Family[sial_seed_set_final$Treatment=="CAAN 50%"] <- "Solanaceae"
sial_seed_set_final$Family[sial_seed_set_final$Treatment=="SOLY 50%"] <- "Solanaceae"
sial_seed_set_final$Family[sial_seed_set_final$Treatment=="SOME 50%"] <- "Solanaceae"
sial_seed_set_final$Family[sial_seed_set_final$Treatment=="PEIN 50%"] <- "Solanaceae"
sial_seed_set_final$Family[sial_seed_set_final$Treatment=="IPPU 50%"] <- "Convolvulaceae"
sial_seed_set_final$Family[sial_seed_set_final$Treatment=="IPAQ 50%"] <- "Convolvulaceae"

sial_seed_set_final$Treatment[sial_seed_set_final$Treatment=="BROL 50%"] <- "Brassica oleracea"
sial_seed_set_final$Treatment[sial_seed_set_final$Treatment=="BRRA 50%"] <- "Brassica rapa"
sial_seed_set_final$Treatment[sial_seed_set_final$Treatment=="CAAN 50%"] <- "Capsicum annuum"
sial_seed_set_final$Treatment[sial_seed_set_final$Treatment=="ERSA 50%"] <- "Eruca vesicaria" #Eruca sativa seems to be a synonym
sial_seed_set_final$Treatment[sial_seed_set_final$Treatment=="IPAQ 50%"] <- "Ipomoea aquatica"
sial_seed_set_final$Treatment[sial_seed_set_final$Treatment=="IPPU 50%"] <- "Ipomoea purpurea"
sial_seed_set_final$Treatment[sial_seed_set_final$Treatment=="PEIN 50%"] <- "Petunia integrifolia"
sial_seed_set_final$Treatment[sial_seed_set_final$Treatment=="SIAL 50%"] <- "Sinapis alba"
sial_seed_set_final$Treatment[sial_seed_set_final$Treatment=="SOLY 50%"] <- "Solanum lycopersicum"
sial_seed_set_final$Treatment[sial_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"
sial_seed_set_final$Treatment[sial_seed_set_final$Treatment=="FC"] <- "Flower control"

sial_seed_set_brassicaceae <- filter(sial_seed_set_final, Family %in% c("Brassicaceae"))
sial_seed_set_convolvulaceae <- filter(sial_seed_set_final, Family %in% c("Convolvulaceae"))
sial_seed_set_solanaceae <- filter(sial_seed_set_final, Family %in% c("Solanaceae"))
sial_seed_set_final$Family[is.na(sial_seed_set_final$Family)] <- "Solanum lycopersicum"

sial_seed_set_cross=sial_seed_set_cross[,-c(5,6)]
sial_seed_set_cross$Family <- "other"
sial_seed_set_self=sial_seed_set_self[,-c(5,6)]
sial_seed_set_self$Family <- "other"
sial_seed_set_control=sial_seed_set_control[,-c(5,6)]
sial_seed_set_control$Family <- "other"
sial_seed_set_flower=sial_seed_set_flower[,-c(5,6)]
sial_seed_set_flower$Family <- "other"

sial_seed_set_final=rbind(sial_seed_set_brassicaceae, sial_seed_set_convolvulaceae, 
                          sial_seed_set_solanaceae, sial_seed_set_cross, sial_seed_set_self, sial_seed_set_control,
                          sial_seed_set_flower)

#Different colour per family
d <- ggplot(sial_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
  labs(title="Sinapis alba",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")

@@

```
```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=3.7, fig.width=7,out.width='100%'}

@@

#Preparing seed set plots, starting with Petunia
#
##
###
#I. AQUATICA
###
##
#

ipaq_seed_set <- read.csv("Data/ipaq_seed_set.csv", sep=";")
colnames(ipaq_seed_set)[1] <- "Species"
colnames(ipaq_seed_set)[2] <- "Treatment"
colnames(ipaq_seed_set)[3] <- "Treatment.number"
colnames(ipaq_seed_set)[4] <- "Seed.production"

ipaq_seed_set <- filter(ipaq_seed_set, Treatment!="RARA 100%" & Treatment!="RARA 50%"& Treatment!="COSA 50%"& Treatment!="COSA 100%" )

#adding the focal species, first 50%
Species <- rep("IPAQ", 10)
Treatment <- rep("IPAQ 50%", 10)
Treatment.number <- seq(1:10)
Seed.production <- rep(0, 10)
ipaq_50 <- data.frame(Species,Treatment, Treatment.number, Seed.production)
#adding the focal species, 100%
Species <- rep("IPAQ", 10)
Treatment <- rep("IPAQ 100%", 10)
Treatment.number <- seq(1:10)
Seed.production <- rep(0, 10)
ipaq_100<-  data.frame(Species,Treatment, Treatment.number, Seed.production)
#Order from lower to higher values the average, to plot it nicely

ipaq_seed_set <- rbind(ipaq_seed_set, ipaq_50, ipaq_100)
ipaq_seed_set$Treatment<- as.character(ipaq_seed_set$Treatment)
ipaq_seed_set <- ipaq_seed_set[order(ipaq_seed_set$Treatment),]

#Organizing with just 50% and cross, self, flower control and control on a side

library(stringr)
ipaq_seed_set_div <- str_split_fixed(as.character(ipaq_seed_set$Treatment), " ", 2)
ipaq_seed_set_div <- data.frame(ipaq_seed_set_div, stringsAsFactors = F)
colnames(ipaq_seed_set_div)=c("non_focal","percentage")
ipaq_seed_set_bind <- cbind(ipaq_seed_set,ipaq_seed_set_div)
ipaq_seed_set_bind <- filter(ipaq_seed_set_bind, percentage!="100%")

#Because I want to give it specifically order I do it separately
#pein_seed_set_common <- filter(ipaq_seed_set_bind, non_focal %in% c("CROSS", "SELF","CONTROL","FLOWER"))

ipaq_seed_set_cross <- filter(ipaq_seed_set_bind, Treatment %in% c("cross"))
ipaq_seed_set_self <- filter(ipaq_seed_set_bind, Treatment %in% c("self"))
ipaq_seed_set_control <- filter(ipaq_seed_set_bind, Treatment %in% c("control"))
ipaq_seed_set_flower <- filter(ipaq_seed_set_bind, Treatment %in% c("flower control"))

#Changing 0 for NA'S FOCAL species

# I HAVENT BEEN ABLE TO WORK OUT ALL AT THE SAME TIME SO i DO IOT SEPARATELY
ipaq_seed_set_bind=ipaq_seed_set_bind[ipaq_seed_set_bind$Treatment!=c("cross"),]
ipaq_seed_set_bind=ipaq_seed_set_bind[ipaq_seed_set_bind$Treatment!=c("self"),]
ipaq_seed_set_bind=ipaq_seed_set_bind[ipaq_seed_set_bind$Treatment!=c("control"),]
ipaq_seed_set_bind=ipaq_seed_set_bind[ipaq_seed_set_bind$Treatment!=c("flower control"),]

ipaq_seed_set_final<-rbind(ipaq_seed_set_bind,ipaq_seed_set_cross, ipaq_seed_set_self, ipaq_seed_set_control,
                           ipaq_seed_set_flower)
#deleting extra columns used for data formating
ipaq_seed_set_final=ipaq_seed_set_final[,-c(5,6)]
#adding NA'S to the focal species
ipaq_seed_set_final[ipaq_seed_set_final$Treatment==c("IPPA 50%"),4] <- NA

#changing non_focal species name
ipaq_seed_set_final$Treatment=as.character(ipaq_seed_set_final$Treatment)
ipaq_seed_set_final$Family[ipaq_seed_set_final$Treatment=="BROL 50%"] <- "Brassicaceae"
ipaq_seed_set_final$Family[ipaq_seed_set_final$Treatment=="BRRA 50%"] <- "Brassicaceae"
ipaq_seed_set_final$Family[ipaq_seed_set_final$Treatment=="SIAL 50%"] <- "Brassicaceae"
ipaq_seed_set_final$Family[ipaq_seed_set_final$Treatment=="ERSA 50%"] <- "Brassicaceae"
ipaq_seed_set_final$Family[ipaq_seed_set_final$Treatment=="CAAN 50%"] <- "Solanaceae"
ipaq_seed_set_final$Family[ipaq_seed_set_final$Treatment=="SOLY 50%"] <- "Solanaceae"
ipaq_seed_set_final$Family[ipaq_seed_set_final$Treatment=="SOME 50%"] <- "Solanaceae"
ipaq_seed_set_final$Family[ipaq_seed_set_final$Treatment=="PEIN 50%"] <- "Solanaceae"
ipaq_seed_set_final$Family[ipaq_seed_set_final$Treatment=="IPPU 50%"] <- "Convolvulaceae"
ipaq_seed_set_final$Family[ipaq_seed_set_final$Treatment=="IPAQ 50%"] <- "Convolvulaceae"

ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="BROL 50%"] <- "Brassica oleracea"
ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="BRRA 50%"] <- "Brassica rapa"
ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="CAAN 50%"] <- "Capsicum annuum"
ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="ERSA 50%"] <- "Eruca vesicaria" #Eruca sativa seems to be a synonym
ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="IPAQ 50%"] <- "Ipomoea aquatica"
ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="IPPU 50%"] <- "Ipomoea purpurea"
ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="PEIN 50%"] <- "Petunia integrifolia"
ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="SIAL 50%"] <- "Sinapis alba"
ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="SOLY 50%"] <- "Solanum lycopersicum"
ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"

ipaq_seed_set_brassicaceae <- filter(ipaq_seed_set_final, Family %in% c("Brassicaceae"))
ipaq_seed_set_convolvulaceae <- filter(ipaq_seed_set_final, Family %in% c("Convolvulaceae"))
ipaq_seed_set_solanaceae <- filter(ipaq_seed_set_final, Family %in% c("Solanaceae"))
ipaq_seed_set_final$Family[is.na(ipaq_seed_set_final$Family)] <- "Solanum lycopersicum"

ipaq_seed_set_cross=ipaq_seed_set_cross[,-c(5,6)]
ipaq_seed_set_cross$Family <- "other"
ipaq_seed_set_self=ipaq_seed_set_self[,-c(5,6)]
ipaq_seed_set_self$Family <- "other"
ipaq_seed_set_control=ipaq_seed_set_control[,-c(5,6)]
ipaq_seed_set_control$Family <- "other"
ipaq_seed_set_flower=ipaq_seed_set_flower[,-c(5,6)]
ipaq_seed_set_flower$Family <- "other"

ipaq_seed_set_final=rbind(ipaq_seed_set_brassicaceae, ipaq_seed_set_convolvulaceae, 
                          ipaq_seed_set_solanaceae, ipaq_seed_set_cross, ipaq_seed_set_self, ipaq_seed_set_control,
                          ipaq_seed_set_flower)

ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="cross"] <- "Cross"
ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="self"] <- "Self"
ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="control"] <- "Control"
ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="flower control"] <- "Flower control"
#Different colour per family
a <- ggplot(ipaq_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
  labs(title="Ipomoea aquatica",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")

ippu_seed_set <- read.csv("Data/ippu_seed_set.csv", sep=";")
colnames(ippu_seed_set)[1] <- "Species"
colnames(ippu_seed_set)[2] <- "Treatment"
colnames(ippu_seed_set)[3] <- "Treatment.number"
colnames(ippu_seed_set)[4] <- "Seed.production"

ippu_seed_set <- filter(ippu_seed_set, Treatment!="RARA 100%" & Treatment!="RARA 50%"& Treatment!="COSA 50%"& Treatment!="COSA 100%" )

#adding the focal species, first 50%
Species <- rep("IPPU", 10)
Treatment <- rep("IPPU 50%", 10)
Treatment.number <- seq(1:10)
Seed.production <- rep(0, 10)
ippu_50 <- data.frame(Species,Treatment, Treatment.number, Seed.production)
#adding the focal species, 100%
Species <- rep("IPPU", 10)
Treatment <- rep("IPPU 100%", 10)
Treatment.number <- seq(1:10)
Seed.production <- rep(0, 10)
ippu_100<-  data.frame(Species,Treatment, Treatment.number, Seed.production)
#Order from lower to higher values the average, to plot it nicely

ippu_seed_set <- rbind(ippu_seed_set, ippu_50, ippu_100)
ippu_seed_set$Treatment<- as.character(ippu_seed_set$Treatment)
ippu_seed_set <- ippu_seed_set[order(ippu_seed_set$Treatment),]

#Organizing with just 50% and cross, self, flower control and control on a side

library(stringr)
ippu_seed_set_div <- str_split_fixed(as.character(ippu_seed_set$Treatment), " ", 2)
ippu_seed_set_div <- data.frame(ippu_seed_set_div, stringsAsFactors = F)
colnames(ippu_seed_set_div)=c("non_focal","percentage")
ippu_seed_set_bind <- cbind(ippu_seed_set,ippu_seed_set_div)
ippu_seed_set_bind <- filter(ippu_seed_set_bind, percentage!="100%")

#Because I want to give it specifically order I do it separately
#pein_seed_set_common <- filter(ippu_seed_set_bind, non_focal %in% c("CROSS", "SELF","CONTROL","FLOWER"))

ippu_seed_set_cross <- filter(ippu_seed_set_bind, Treatment %in% c("cross"))
ippu_seed_set_self <- filter(ippu_seed_set_bind, Treatment %in% c("self"))
ippu_seed_set_control <- filter(ippu_seed_set_bind, Treatment %in% c("control"))
ippu_seed_set_flower <- filter(ippu_seed_set_bind, Treatment %in% c("flower control"))

#Changing 0 for NA'S FOCAL species

# I HAVENT BEEN ABLE TO WORK OUT ALL AT THE SAME TIME SO i DO IOT SEPARATELY
ippu_seed_set_bind=ippu_seed_set_bind[ippu_seed_set_bind$Treatment!=c("cross"),]
ippu_seed_set_bind=ippu_seed_set_bind[ippu_seed_set_bind$Treatment!=c("self"),]
ippu_seed_set_bind=ippu_seed_set_bind[ippu_seed_set_bind$Treatment!=c("control"),]
ippu_seed_set_bind=ippu_seed_set_bind[ippu_seed_set_bind$Treatment!=c("flower control"),]

ippu_seed_set_final<-rbind(ippu_seed_set_bind,ippu_seed_set_cross, ippu_seed_set_self, ippu_seed_set_control,
                           ippu_seed_set_flower)
#deleting extra columns used for data formating
ippu_seed_set_final=ippu_seed_set_final[,-c(5,6)]
#adding NA'S to the focal species
ippu_seed_set_final[ippu_seed_set_final$Treatment==c("IPPU 50%"),4] <- NA

#changing non_focal species name
ippu_seed_set_final$Treatment=as.character(ippu_seed_set_final$Treatment)
ippu_seed_set_final$Family[ippu_seed_set_final$Treatment=="BROL 50%"] <- "Brassicaceae"
ippu_seed_set_final$Family[ippu_seed_set_final$Treatment=="BRRA 50%"] <- "Brassicaceae"
ippu_seed_set_final$Family[ippu_seed_set_final$Treatment=="SIAL 50%"] <- "Brassicaceae"
ippu_seed_set_final$Family[ippu_seed_set_final$Treatment=="ERSA 50%"] <- "Brassicaceae"
ippu_seed_set_final$Family[ippu_seed_set_final$Treatment=="CAAN 50%"] <- "Solanaceae"
ippu_seed_set_final$Family[ippu_seed_set_final$Treatment=="SOLY 50%"] <- "Solanaceae"
ippu_seed_set_final$Family[ippu_seed_set_final$Treatment=="SOME 50%"] <- "Solanaceae"
ippu_seed_set_final$Family[ippu_seed_set_final$Treatment=="PEIN 50%"] <- "Solanaceae"
ippu_seed_set_final$Family[ippu_seed_set_final$Treatment=="IPPU 50%"] <- "Convolvulaceae"
ippu_seed_set_final$Family[ippu_seed_set_final$Treatment=="IPAQ 50%"] <- "Convolvulaceae"

>>>>

#There are 3 crosses were seeds were lost (2,7,9)
#load libraries
library(reshape2)
library(ggplot2)
library(dplyr)
library(gridExtra)
library(grid)
library(lattice)
#read data and cleaning
pein_seed_set_final <- read.csv("Data/pein_seed_set_final_common_names.csv")
pein_seed_set_final=pein_seed_set_final[,-1]
#load the palette for all the 4 plots
cbPalette <- c( "#56B4E9","#E69F00", "#999999", "#009E73")
#Colur per family

a <- ggplot(pein_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
  labs(title="Petunia",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x =element_blank())+
  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")

@@

#Colur per family
#Different colour per family
b <- ggplot(caan_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
  labs(title="Capsicum",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x =element_blank())+
  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")

@@

soly_seed_set_final <- read.csv("Data/soly_seed_set_final_common_names.csv")
soly_seed_set_final=soly_seed_set_final[,-1]

cbPalette <- c( "#56B4E9","#E69F00", "#999999", "#009E73")
#Different colour per family
c <- ggplot(soly_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
  labs(title="Tomato",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")

@@

some_seed_set_final <- read.csv("Data/some_seed_set_final_common_names.csv")
some_seed_set_final=some_seed_set_final[,-1]

#Different colour per family
d <- ggplot(some_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
  labs(title="Eggplant",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")

@@

brol_seed_set_final <- read.csv("Data/brol_seed_set_final.csv")
brol_seed_set_final=brol_seed_set_final[,-1]
#Different colour per family
a <- ggplot(brol_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
  labs(title="Wild cabagge",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x =element_blank())+
  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")

@@

#Different colour per family
b <- ggplot(brra_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
  labs(title="Pak choi",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x =element_blank())+
  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")

@@

ersa_seed_set_final <- read.csv("Data/ersa_seed_set_final_common_names.csv")
ersa_seed_set_final=ersa_seed_set_final[,-1]

#Different colour per family
c <- ggplot(ersa_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
  labs(title="Rocket",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")

@@

sial_seed_set_final <- read.csv("Data/sial_seed_set_final_common_names.csv")
sial_seed_set_final=sial_seed_set_final[,-1]

#Different colour per family
d <- ggplot(sial_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
  labs(title="White mustard",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")

@@

\newpage
```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=3.7, fig.width=7,out.width='100%'}

@@

#Preparing seed set plots, starting with Petunia
#
##
###
#I. AQUATICA
###
##
#
ipaq_seed_set_final <- read.csv("Data/ipaq_seed_set_final_common_names.csv")
ipaq_seed_set_final=ipaq_seed_set_final[,-1]

cbPalette <- c( "#56B4E9","#E69F00", "#999999", "#009E73")

#Different colour per family
a <- ggplot(ipaq_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
  labs(title="Ipomoea aquatica",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")

#IPPU
ippu_seed_set_final <- read.csv("Data/ippu_seed_set_final_common_names.csv")
ippu_seed_set_final=ippu_seed_set_final[,-1]
